---
title: "ecommerce_purchase_solutions in R"
author: "Sripad Kulkarni"
date: "24/11/2020"
output: pdf_document
---

```{r setup, include=FALSE, echo=FALSE, cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### load the libraries
```{r message=FALSE, warning=FALSE}
pacman::p_load(tidyverse, stringr)
```


### load the dataset
```{r message=FALSE, warning=FALSE}
ecom <- read_csv("/Users/sripadk/Desktop/Ecommerce")
head(ecom)
```
### What is the average Purchase Price?
```{r message=FALSE, warning=FALSE}
mean(ecom$`Purchase Price`, na.rm = T)
```

### What were the highest and lowest purchase prices? **
```{r message=FALSE, warning=FALSE}
max(ecom$`Purchase Price`, na.rm = T)
```

```{r message=FALSE, warning=FALSE}
min(ecom$`Purchase Price`, na.rm = T)
```

### How many people have English 'en' as their Language of choice on the website?
```{r message=FALSE, warning=FALSE}
ecom %>% 
  filter(Language == 'en') %>% 
  count()
```

### How many people have the job title of "Lawyer" ? **
```{r message=FALSE, warning=FALSE}
ecom %>% 
  filter(Job == 'Lawyer') %>% 
  count()
```

### How many people made the purchase during the AM and how many people made the purchase during PM ?
```{r message=FALSE, warning=FALSE}
ecom %>% 
  count(`AM or PM`) %>% 
  ungroup()
```

### What are the 5 most common Job Titles?
```{r message=FALSE, warning=FALSE}
ecom %>% 
  count(Job, sort = T) %>% 
  head(5)
```

### Someone made a purchase that came from Lot: "90 WT" , what was the Purchase Price for this transaction?
```{r message=FALSE, warning=FALSE}
ecom %>% 
  filter(Lot == '90 WT') %>% 
  select(`Purchase Price`)
```

### What is the email of the person with the following Credit Card Number: 4926535242672853
```{r message=FALSE, warning=FALSE}
ecom %>% 
  filter(`Credit Card` == 4926535242672853) %>% 
  select(`Email`)
```

### How many people have American Express as their Credit Card Provider *and* made a purchase above $95 ?
```{r message=FALSE, warning=FALSE}
ecom %>% 
  filter(`CC Provider` == 'American Express' & `Purchase Price` > 95) %>% 
  count()
```

### How many people have a credit card that expires in 2025?
```{r message=FALSE, warning=FALSE}
sum(str_count(ecom$`CC Exp Date`, '25' ))
```

### Hard: What are the top 5 most popular email providers/hosts
```{r message=FALSE, warning=FALSE}
ecom %>% 
  mutate(domain = sub('.*@', "",ecom$Email)) %>% 
  count(domain, sort = T) %>% 
  head(5)
```
