---
title: "salaries_solutions in R"
author: "Sripad Kulkarni"
date: "11/20/2020"
output: pdf_document
---

```{r setup, include=FALSE, echo=FALSE, cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### load the libraries
```{r message=FALSE, warning=FALSE}
pacman::p_load(tidyverse, stringr)
```


### load the dataset
```{r message=FALSE, warning=FALSE}
sal <- read_csv("/Users/sripadk/Desktop/Salaries.csv")
head(sal)
```

### Average Basepay
```{r message=FALSE, warning=FALSE}
mean(sal$BasePay, na.rm = T)
```

### What is the highest amount of OvertimePay in the dataset?
```{r message=FALSE, warning=FALSE}
max(sal$OvertimePay, na.rm = T)
```

### What is the job title of JOSEPH DRISCOLL ?
```{r message=FALSE, warning=FALSE}
sal %>% 
  filter(EmployeeName == 'JOSEPH DRISCOLL') %>% 
  select(Id, JobTitle)
```

### How much does JOSEPH DRISCOLL make (including benefits)? 
```{r message=FALSE, warning=FALSE}
sal %>% 
  filter(EmployeeName == 'JOSEPH DRISCOLL') %>% 
  select(TotalPayBenefits)
```

### What is the name of highest paid person (including benefits)? 
```{r message=FALSE, warning=FALSE}
sal %>% 
  filter(TotalPayBenefits == max(TotalPayBenefits))
```

### What is the name of lowest paid person (including benefits)? 
```{r message=FALSE, warning=FALSE}
sal %>% 
  filter(TotalPayBenefits == min(TotalPayBenefits))
```

### What was the average (mean) BasePay of all employees per year? (2011-2014) ?
```{r message=FALSE, warning=FALSE}
sal %>% 
  group_by(Year) %>% 
  summarise(mean_base_pay = mean(BasePay, na.rm = TRUE)) %>% 
  ungroup()
```

### How many unique job titles are there?
```{r message=FALSE, warning=FALSE}
sal %>% 
  summarise(unique_title = n_distinct(JobTitle))
```

### What are the top 5 most common jobs?
```{r message=FALSE, warning=FALSE}
sal %>% 
  group_by(JobTitle) %>% 
  summarise(ct = n_distinct(Id)) %>% 
  arrange(desc(ct)) %>% 
  head(5) %>% 
  ungroup()
```

### How many people have the word Chief in their job title?
```{r message=FALSE, warning=FALSE}
sal %>% 
  mutate(JobTitle = tolower(JobTitle)) %>% 
  summarise(ct = sum(str_detect(JobTitle, "chief")))
```

### Is there a correlation between length of the Job Title string and Salary?
```{r message=FALSE, warning=FALSE}
cor(str_count(sal$JobTitle), sal$TotalPayBenefits)
```
